Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-21 cordillera-cycle.tex
Rev. Jarosch: add rel. errors to in discussion.
Moderate ice volume estimate by stating uncertainties from the sensitivity tests.

      Using the GRIP ice core palaeo-temperature record as climate forcing
      time-series, the model shows a significant sensitivity to selected ice
      rheologic and basal sliding parameters (Fig.~\ref{fig:sens_ts};
      Table~\ref{tab:sens_extrema}) in terms of modelled ice extent, and
      even more so in terms of modelled ice volumes.

@@

      During MIS~2, the modelled total ice volume peaks at
      8.62\,\unit{m}\,s.l.e. (19.1\,\unit{ka}) in the GRIP simulation and at
      8.56\,\unit{m}\,s.l.e. (17.4\,\unit{ka}) in the EPICA simulation.

@@

      During MIS~4, the modelled total ice volume peaks at
      7.43\,\unit{m}\,s.l.e. (57.6\,\unit{ka}) in the GRIP simulation and at
      4.84\,\unit{m}\,s.l.e. (61.9\,\unit{ka}) in the EPICA simulation,
      corresponding to respectively 86 and 57\,\unit{\%} of modelled MIS~2
      ice volumes.

@@

      The modelled total ice volume corresponding to these persistent
      ice-dispersal centres attains a~minimum of 1.54\,\unit{m}\,s.l.e.
      (42.9\,\unit{ka}) in the GRIP simulation and of 2.55\,\unit{m}\,s.l.e.
      (52.4\,\unit{ka}) in the EPICA simulation, corresponding to
      respectively 18 and 30\,\unit{\%} of the MIS~2 ice volumes.

>>>>

      Using the GRIP ice core palaeo-temperature record as climate forcing
      time-series, the model shows a significant sensitivity to selected ice
      rheological and basal sliding parameters (Fig.~\ref{fig:sens_ts};
      Table~\ref{tab:sens_extrema}) in terms of modelled ice extent, and
      even more so in terms of modelled ice volumes.

@@

      During MIS~2, the modelled total ice volume peaks at
      8.62\,\unit{m}\,s.l.e. (19.1\,\unit{ka}) in the GRIP simulation and at
      8.56\,\unit{m}\,s.l.e. (17.4\,\unit{ka}) in the EPICA simulation.
      However, these numers are subject to uncertainties on physics
      embedded in the model. The range of parameter values tested in our
      sensitivity study on the lower-resolution GRIP simulation
      (Sect.~\ref{sec:sens}) yielded relative errors of 30\,\unit{\%}
      regarding ice rheological parameters and 21\,\unit{\%} regarding basal
      sliding parameters (Fig.~\ref{fig:sens_ts};
      Table~\ref{tab:sens_extrema}).

@@

      During MIS~4, the modelled total ice volume peaks at
      7.43\,\unit{m}\,s.l.e. (57.6\,\unit{ka}) in the GRIP simulation and at
      4.84\,\unit{m}\,s.l.e. (61.9\,\unit{ka}) in the EPICA simulation,
      corresponding to respectively 86 and 57\,\unit{\%} of modelled MIS~2
      ice volumes.
      These estimates appear little sensitive to the range of parameter
      values tested in our sensitivity study (Sect.~\ref{sec:sens}), which
      yielded relative errors of 17\,\unit{\%} to ice rheological parameters
      and 21\,\unit{\%} to basal sliding parameters
      (Fig.~\ref{fig:sens_ts}; Table~\ref{tab:sens_extrema}).

@@

      The modelled total ice volume corresponding to these persistent
      ice-dispersal centres attains a~minimum of 1.54\,\unit{m}\,s.l.e.
      (42.9\,\unit{ka}) in the GRIP simulation and of 2.55\,\unit{m}\,s.l.e.
      (52.4\,\unit{ka}) in the EPICA simulation, corresponding to
      respectively 18 and 30\,\unit{\%} of the MIS~2 ice volumes.
      However, these numbers should be considered with caution as our
      sensitivity study (Sect.~\ref{sec:sens}) shows that minimum ice volume
      during MIS~3 is highly sensitive to ice flow parameters, with relative
      errors of 57\,\unit{\%} to the range of ice rheological parameters
      tested and 120\,\unit{\%} to the range of basal sliding parameters
      tested (Fig.~\ref{fig:sens_ts}; Table~\ref{tab:sens_extrema}).
